

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo = FALSE, eval = FALSE}
rmarkdown:: render("2021-10-03-Project 1.rmd",
                   output_format = "github_document",
                   output_dir = "../_posts",
                   output_options = list(html_preview = FALSE, keep_html = FALSE)
                   )
```


For Project 1 I created a vignette about contacting an API. Data from
the Covid 19 API was utilized for the project. For the project I created
functions to query, parse, and return structured data from the API. I
don’t have a lot of experience working with APIs and I have never
created a vignette. The learning experience was the interesting and
difficult part of the project for me.

The most difficult part of the project for me was understanding how to
create user defined functions to query the API. It was also kind of
difficult to get meaningful data for the Data Analysis part of the
vignette. To remedy this I often combined data from different endpoints.

If I had to do a similar project in the future I would make sure I was
well versed on contacting APIs and creating functions to query APIs. I would
also make sure I had adequate time to research the API and get familiar
with it.  Here is the link to my github pages repo for the project [link] (https://github.com/ChennadeBrown/Project1-558) and here is the link to my usual repo [link] (https://github.com/ChennadeBrown/ChennadeBrown.github.io).

